Tropical Andes plant occurrence data GBIF

### 2023-10-17 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
add subset to Tropical Andes habitat shape code, update object names

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0001452-230918134249559", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

# Summary 
```{r}
glimpse(d1)
```

```{r}
print("The number of occurrences is")
nrow(d1)
print("The number of species is" )
length(unique(d1$species))
print("The number of genera is" )
length(unique(d1$genus))
print("The number of families is" )
length(unique(d1$family))
```

# Extract species list
```{r}
GBIF_SpeciesList <- unique(d1$species)
```

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropicalAndes_GBIF_plant_occ.csv") 
write.csv(d1, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropicalAndes_GBIF_plant_species.csv") 
write.csv(GBIF_SpeciesList, file = TropicalAndes_GBIF_species_path)
```

>>>>

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0009835-231002084531237", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

# Subset occurrence to Tropical Andes IUCN Montane and Lowland forest

## Read in Forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path, "Forest_sf.shp"), layer = "Forest_sf")
```

## Convert data frame to sf object
```{r}
TropicalAndes_plant_occ <- st_as_sf(x = d1, 
                        coords = c("decimalLongitude", "decimalLatitude"),
                        crs = "+proj=longlat +datum=WGS84 +no_defs")
```

# Crop occurrence data to forest extent
```{r}
TropicalAndes_plant_occ_forest <- TropicalAndes_plant_occ[Forest_sf,]
```

# Summary 
```{r}
glimpse(TropicalAndes_plant_occ_forest)
```

```{r}
print("The number of occurrences is")
nrow(TropicalAndes_plant_occ_forest)
print("The number of species is" )
length(unique(TropicalAndes_plant_occ_forest$species))
print("The number of genera is" )
length(unique(TropicalAndes_plant_occ_forest$genus))
print("The number of families is" )
length(unique(TropicalAndes_plant_occ_forest$family))
```

# Extract species list
```{r}
GBIF_SpeciesList <- unique(TropicalAndes_plant_occ_forest$species)
```

# Write data to csv
```{r}
write.csv(TropicalAndes_plant_occ_forest, file.path(output_path,"TropicalAndes_GBIF_plant_occ.csv"))

write.csv(GBIF_SpeciesList, file.path(output_path,"TropicalAndes_GBIF_plant_species.csv"))
```
